### 2017-05-31 paper.tex
Merging and editing

The software community's model of collaborative code development is an alternative.
The authors first encountered it in the context of
lessons on basic lab skills for research computing
in the sciences and humanities. They primarily draw on 
their experiences with pedagogical organizations such as 
Software Carpentry and Programming Historian. 
Software Carpentry was founded in 1998 with the goal of 
``making scientists more productive, and their work more
reliable, by teaching them basic computing skills.'' 
They do so through short one or two day intensive workshops that
cover the basics of scientific computing. Programming Historian 
was founded in 2008, and has evolved to become a collaboratively edited
site providing lessons to humanists.

In this article, we strive for an open-source software model, 
by which we mean lesson materials that are:

@@

\item
  Open and easily accessible

\item
  Continually maintained, refined, and 
  improved by a community of contributors

@@

To our knowledge, Software Carpentry (and its related
organizations such as Data Carpentry) are the only real-world
example of an organization satisfying these criteria. Programming
Historian, and other open educational resources, satisfy the
first criteria but not necessarily the latter. While they 
might experience a kind of iterative development where the 
lessons are periodically updated by a small author group
(e.g. this happens when a new edition of an academic 
textbook is released), but this is not the same as regular, 
small releases from a large community of contributors.

Meeting both criteria is critical for two reasons. We need
lessons that are up-to-date with the latest information,
which is crucial given the speed of software development. A lag
between editions means broken dependencies and bugs. Second, lessons
need to continue to live after a key author moves on from 
being able to maintain the lesson.

>>>>

The software community's model of collaborative code development is an alternative.
The authors first encountered it in the context of
lessons on basic lab skills for research computing
in the sciences and humanities. They primarily draw on
their experiences with pedagogical organizations such as
Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998
to make scientists more productive,
and their work more reliable,
by teaching them basic computing skills.
It has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanists.

These organizations have been successful in adapting open source development methods
to the problem of lesson development and maintenance.
Their guiding principles are that lessons should be:

@@

\item
  open and easily accessible, and

\item
  continually maintained, refined, and improved
  by a community of contributors.

@@

Many open education projects satisfy the first criterion,
but very few satisfy the second.
While their lessons might periodically be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as regular, small releases
from a large community of contributors.

Meeting both criteria is critical for two reasons.
We need lessons that are up-to-date with the latest information,
which is crucial given the speed of software development.
A lag between editions means broken dependencies and bugs.
Second,
lessons need to continue to live after a key author moves on
from being able to maintain them.
